---
title: "Exercise 1.1"
author: "Shunyi Huang"
date: "2022/9/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading packages and importing data

```{r cars}
library(tidyverse)
library(ggplot2)
library(dplyr)
temperature <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/data/temperatures.csv")
head(temperature,3)
```


Q1: Version of figure 
```{r}
ggplot(temperature, aes(x = date, y = temperature, group = city, colour = city, lw = 5))+
  geom_line()
```



```{r}
ggplot(temperature)+
  geom_line(aes(date, temperature, col = city),size = 1)+
  scale_x_date(date_labels = '%B')
```


 Q2: group_by + summarise

```{r}
temp_df = temperature %>% group_by(city,month) %>% summarise(mean = mean(temperature))
temp_df
```


Q3: Version figure 2.4
```{r}
ggplot(temp_df, aes(x = month, y = city, fill = mean, reorder(city,mean))) +
  geom_tile(colour="white", size=2) + 
  theme_bw() + 
  scale_fill_gradient(low = "#353436",
                    high = "#f6f805",
                    guide = "colorbar") +
  coord_fixed()
```

Q4: Compare and Contrast two displays.
From my point of view, the line plot might be easier for us to visualize. Because the geon_tile is pretty much the same as heatmap and it takes effort to modify the color for better visualization, thus line plot is faster to make.
Figure 2.3 (lineplot) tells user the distribution, and enable the view of short/long term trend
Figure 2.4 (heatmap) tells user the correlation among the three features.




