---
title: "Exercise 2.1"
author: "Shunyi Huang"
date: "2022/9/7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1: Provide server code which would allow the scatterplot to update the highlighted athletes depending
on the currently selected sports.

```{r}
library(shiny)
library(tidyverse)
olympics <- read_csv("https://uwmadison.box.com/shared/static/rzw8h2x6dp5693gdbpgxaf2koqijo12l.csv")
#' Scatterplot with highlighted points
#'
#' Assumes a column in df called "selected" saying whether points should be
#' larger / darker
# scatterplot <- function(df) {
#   ggplot(df) +
#     geom_point(
#     aes(Weight, `Height, cm`,
#     alpha = as.numeric(selected),
#     size = as.numeric(selected))
#     ) +
#     scale_alpha(range = c(0.05, .8)) +
#     scale_size(range = c(0.1, 1))
# }

#olympics$selected = sample(1, size = nrow(olympics), replace = TRUE)
olympics$selected = runif(nrow(olympics), 0, 1)
scatterplot <- function(df) {
  ggplot(df) +
    geom_point(
    aes(Weight, `Height, cm`,
    alpha = as.numeric(selected),
    size = as.numeric(selected)))+
    scale_alpha(range = c(0.05, .8)) +
    scale_size(range = c(0.1, 1))
}

```


```{r}
#' Assumes a column in df called "selected" saying whether points should be
#' larger / darker

ui <- fluidPage(
  #Front end interface
  selectInput("dropdown", "Select a Sport", choices = unique(olympics$Sport), multiple = TRUE),
  plotOutput("scatterplot"),
  dataTableOutput('table')
)

server <- function(input, output) {
  #Back end logic
  # cur_data <- reactive({
  #   sports_name = input$dropdown
  #   print(sports_name)
  #   olympics$selected = 0
  #   olympics$selected[which(olympics$Sport %in% sports_name)] = 1
  # })
  
  olymp_sub <- reactive({
    olympics%>%mutate(selected=1 * (Sport %in% input$dropdown))
  })
  
  output$scatterplot <- renderPlot({
    # olympics$selected = 0
    # olympics$selected[which(olympics$Sport %in% input$dropdown)] = 1
    scatterplot(olymp_sub())
  })
  
  output$table <- renderDataTable({
    # olympics$selected = 0
    # olympics$selected[which(olympics$Sport == input$dropdown)] = 1
    # olympics[olympics$selected == 1,]
    olymp_sub()[olymp_sub()$selected == 1,]
  }
  )
  
}





shinyApp(ui,server)
```
    Describe changes to your solution to (a) to meet the new requirements. How
    would you minimize code duplication? Be as specific as possible.
    
    In (a) I initialized all the values in selected to 0 and the one in dropdown to 1, and this step was used in both creating plot and table. 
    To minimize the code, I used a similar reactive function in the demo from class which only initialized the selected sport to 1 in the selected column but in a different form in shiny

```{r}

```







