---
title: "Penguin 1.1"
name: "Shunyi Huang"
email: "shuang347@wisc.edu"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(tidyverse)
penguins <- read_csv("https://uwmadison.box.com/shared/static/ijh7iipc9ect1jf0z8qa2n3j7dgem1gh.csv")
head(penguins,2)
```



```{r pressure, echo=FALSE}
library(ggplot2)
ggplot(penguins)+
  geom_point(aes(bill_length_mm, bill_depth_mm, colour = species),size = 1)+
  facet_wrap(~ island)

```

```{r}
ggplot(penguins)+
  geom_point(aes(bill_length_mm, bill_depth_mm, colour = species),size = 1)
```



Simpson's paradox:
It is a phenomenon in probability and statistics in which a trend appears in several groups of data but disappears or reverses when the groups are combined
In the first plot above, every island has species Adelie, but when combining the plots together, the trend in each island disappeared. This phemomeonon satisfied the content of Simpson's paradox.
The Adelie specie is around 50%-100% in each plot in the first graph; however, when comes to the second plot, the Adelie specie's porprotion is no longer more than 60%(visually)
